---
title: "Models"
execute: 
  echo: false
---


```{r}
#| message: false
library(tidyverse)
library(patchwork)
```

```{r}
#| message: false
dmg <- read_csv("matchmaking_data/CS_Damage.csv")
```

```{r}
dmg1 <- dmg |> 
  group_by(wp) |>
  summarize(
    total_hp_damage = sum(hp_dmg, na.rm = TRUE),
    average_hp_damage = mean(hp_dmg, na.rm = TRUE),
    count = n()
  ) |> 
  arrange(desc(total_hp_damage))
```
```{r}
weapon_categories <- tribble(
  ~wp,           ~category,
  "AK47",        "Rifle",
  "M4A4",        "Rifle",
  "M4A1",        "Rifle",
  "Famas",       "Rifle",
  "Gallil",      "Rifle",
  "AUG",         "Rifle",
  "SG556",       "Rifle",
  "AWP",         "Sniper",
  "Scout",       "Sniper",
  "Scar20",      "Sniper",
  "G3SG1",       "Sniper",
  "Deagle",      "Pistol",
  "USP",         "Pistol",
  "Glock",       "Pistol",
  "CZ",          "Pistol",
  "P250",        "Pistol",
  "FiveSeven",   "Pistol",
  "P2000",       "Pistol",
  "Tec9",        "Pistol",
  "DualBarettas","Pistol",
  "Zeus",        "Pistol",
  "Revolver",    "Pistol",
  "UMP",         "SMG",
  "Mac10",       "SMG",
  "MP9",         "SMG",
  "MP7",         "SMG",
  "P90",         "SMG",
  "Bizon",       "SMG",
  "Nova",        "Heavy",
  "XM1014",      "Heavy",
  "Swag7",       "Heavy",
  "SawedOff",    "Heavy",
  "M249",        "Heavy",
  "Negev",       "Heavy",
  "HE",          "Grenade",
  "Molotov",     "Grenade",
  "Incendiary",  "Grenade",
  "Smoke",       "Grenade",
  "Flash",       "Grenade",
  "Bomb",        "Grenade"
)
```

```{r}
dmg_full <- dmg1 |> left_join(weapon_categories, by = "wp")

dmg_cat <- split(dmg_full, dmg_full$category)
cat_rifles <- dmg_cat$Rifle
cat_pistols <- dmg_cat$Pistol
cat_sniper <- dmg_cat$Sniper
cat_heavy <- dmg_cat$Heavy
cat_SMG <- dmg_cat$SMG
cat_grenade <- dmg_cat$Grenade
dmg2 <- dmg_full |> filter(!wp %in% c("Smoke", "Flash", "Bomb", "Molotov", 
"Incendiary", "Unknown"))
dmg2 |> 
  ggplot(aes(x = reorder(wp, average_hp_damage), y = average_hp_damage, fill = category)) +
  geom_bar(stat = 'identity') + scale_color_viridis_c() + theme_minimal() +
  theme(axis.text.x = element_text(face = "bold", angle = 45)) +
  labs(
    title = 'Average HP Damage by Weapon',
    x = 'Weapon',
    y = 'Average HP Damage', fill = NULL
  )
```
This graph represents a comparison of the average damage dealt throughout many rounds for every weapon. Some notable observations that could be made for this graph is that the Zeus is a weapon that is designed to one-shot, so it does full health and armor damage every time it hits someone, which is why its damage values are much higher than any other. The snipers are also at the high levels because they have high base damage values.
```{r}
pistol_dmg <- cat_pistols |>  ggplot(aes(x = reorder(wp, average_hp_damage), y = average_hp_damage)) +
  geom_bar(stat = 'identity', width = .7) + 
  theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme_minimal() +
  labs(x = "Pistols", y = NULL)
rifle_dmg <- cat_rifles |>  ggplot(aes(x = reorder(wp, average_hp_damage), y = average_hp_damage)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme_minimal() +
  labs(x = "Rifles", y = "Average HP Damage")
SMG_dmg <- cat_SMG |> ggplot(aes(x = reorder(wp, average_hp_damage), 
  y = average_hp_damage)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme_minimal() +
  labs(x = "SMGs", y = NULL)
heavy_dmg <- cat_heavy |> ggplot(aes(x = reorder(wp, average_hp_damage), 
  y = average_hp_damage)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme_minimal() +
  labs(x = "Heavies", y = NULL)
sniper_dmg <- cat_sniper |>  ggplot(aes(x = reorder(wp, average_hp_damage), 
  y = average_hp_damage)) +
  geom_bar(stat = 'identity') + 
  theme(axis.text.x = element_text(face = "bold", angle = 45)) + theme_minimal() +
  labs(x = "Snipers", y = NULL)
```
# Graphs by category
```{r}
combined_dmg1 <- pistol_dmg / rifle_dmg / sniper_dmg
combined_dmg1
```
These three graphs above show the HP Damage spread for the pistols, rifles, and snipers. Most of these average damage representations have similar trends to the total graph, as weapons with similar base damage values are close to each other in total damage. The AWP has much higher base damage than the other snipers, making it get the highest total damage. 
```{r}
combined_dmg2 <- heavy_dmg / SMG_dmg
combined_dmg2
```

```{r}
#| message: false
kills <- read_csv("matchmaking_data/CS_Kills.csv")
```

```{r}
kills1 <- kills |> 
  group_by(wp) |> 
  summarize(kills = n()) |> 
  arrange(desc(kills))

kills_filtered <- kills1 |>  filter(!wp %in% c("Smoke", "Flash", "Bomb", "Molotov", 
"Incendiary", "Unknown", "World"))

kills_filtered$log_kills <- log10(kills_filtered$kills)

# Heatmap with log-transformed kills
ggplot(kills_filtered, aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Heatmap of Log-Transformed Kills per Weapon", subtitle = "This is logarithmically scaled", x = "Weapon", fill = "Total Kills", y = NULL) +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))


kills_full <- kills_filtered |> left_join(weapon_categories, by = "wp")
kills_cat <- split(kills_full, kills_full$category)
kcat_pistol <- kills_cat$Pistol
kcat_rifle <- kills_cat$Rifle
kcat_sniper <- kills_cat$Sniper
kcat_heavy <- kills_cat$Heavy
kcat_SMG <- kills_cat$SMG

kpistol <- kcat_pistol |> ggplot(aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_color_viridis_b() +
  labs(title = "Pistol Kills", x = "Weapon", y = NULL, fill = "Total Kills") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))
krifle <- kcat_rifle |> ggplot(aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_fill_gradient(low = "#e1f00e", high = "blue") +
  labs(title = "Rifle Kills", x = "Weapon", y = NULL, fill = "Total Kills") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))
ksniper <- kcat_sniper |> ggplot(aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_fill_gradient(low = "#34d1cc", high = "#00eb0c") +
  labs(title = "Sniper Kills", x = "Weapon", y = NULL, fill = "Total Kills") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))
kheavy <- kcat_heavy |> ggplot(aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_fill_gradient(low = "#e1f00e", high = "blue") +
  labs(title = "Heavy Kills", x = "Weapon", y = NULL, fill = "Total Kills") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))
kSMG <- kcat_SMG |> ggplot(aes(x = reorder(wp, log_kills), y = "Kills", fill = log_kills)) +
  geom_tile() +
  scale_fill_gradient(low = "#e1f00e", high = "blue") +
  labs(title = "SMG Kills", x = "Weapon", y = NULL, fill = "Total Kills") +
  theme_minimal() +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), axis.text.x = element_text(face = "bold", angle = 45))
```
```{r}
kpistol

krifle

ksniper

kheavy

kSMG
```





